---
title: "Iteration and List Columns"
output: github_document
---

Load libraries that you will need:

```{r setup}
library(tidyverse)
library(rvest)

set.seed(1)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Lists

```{r}

l =
  list(
    vec_numeric = 5:8,
    vec_logical = c(TRUE, FALSE),
    summary = summary(rnorm(1000, mean = 5, sd = 3))
)

l[[3]]

l[["summary"]]

l$summary
```

## Lists of normals

```{r}
list_norms = 
  list(
    a = rnorm(50, mean = 2, sd = 1),
    b = rnorm(50, mean = 5, sd = 3),
    c = rnorm(50, mean = 20, sd = 1.2),
    d = rnorm(50, mean = -12, sd = 0.5)
  )

mean_sd(list_norms[[1]])
mean_sd(list_norms[["a"]])

```

Here is the mean and standard deviation function from "Writing Functions":
```{r}
mean_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("x needs to be numeric")
    }
  
  if (length(x) <3) {
    stop("x should have at least 3 numbers")
  }

  mean_x = mean(x)
  sd_x = sd(x)
        
  output_df = 
    tibble(
      mean = mean_x,
      sd = sd_x)

  return(output_df)
  
}
```

## for loop

Let's use a for loop to iterate over my list of normals.

```{r}
output = vector("list", length = 4)

output[[1]] = mean_sd(list_norms[[1]])
output

for (i in 1:4){
  
  output[[i]] = mean_sd(list_norms[[i]])

}
```

Let's use map instead...

**Summary gives min, max, IQR, and median
**map_dbl simplifies output, helpful when output is only one number

```{r}
output = map(list_norms, mean_sd)

output = map(list_norms, median)

output = map(list_norms, summary)

output = map(list_norms, IQR)

output = map_dbl(list_norms, median)

```

## LIST COLUMNS!!!!

```{r}
listcol_df = 
  tibble(
    name = c("a", "b", "c", "d"),
    norms = list_norms
  )

listcol_df %>% 
  filter(name == "a")

listcol_df %>% pull(name)
listcol_df %>% pull(norms)

listcol_df$norms[[1]]

mean_sd(listcol_df$norms[[1]])

map(listcol_df$norms, mean_sd)

listcol_df %>% 
  mutate(summaries = map(norms, mean_sd)) %>% 
  pull(summaries)
```


## Nested data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Nest data within location

```{r}
weather_nested = weather_df %>% 
  nest(data = date:tmin)

weather_nested %>% 
  filter(name == "CentralPark_NY") %>% 
  pull(data)

weather_nested %>% 
  pull(data)
```

## Linear regression models

Here we are fitting separate linear regression models for tmax on tmin at each location
```{r}
weather_nested = nest(weather_df, data = date:tmin)

weather_lm = function(df) {
  lm(tmax ~ tmin, data = df)
}

weather_lm(weather_nested$data[[1]])

map(weather_nested$data, weather_lm)

weather_nested %>%
  mutate(lm_results = map(data, weather_lm))
  
```

We can also un-nest data

```{r}
unnest(weather_nested, data)
```

## Napoleon!!

This is the function from the "Writing Functions" Rmd file

```{r}
get_page_reviews = function(page_url){
  
  page_html = read_html(page_url)

  review_titles = 
    page_html %>%
    html_elements(".a-text-bold span") %>%
    html_text()
  
  review_stars = 
    page_html %>%
    html_elements("#cm_cr-review_list .review-rating") %>%
    html_text()
  
  review_text = 
    page_html %>%
    html_elements(".review-text-content span") %>%
    html_text()
  
  reviews = tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
  
  return(reviews)
}

base_url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

urls = str_c(base_url, 1:5)

map(urls, get_page_reviews)

napoleon_df = 
  tibble(
    urls = urls
  )

napoleon_df %>% 
  mutate(reviews = map(urls, get_page_reviews)) %>% 
  select(reviews) %>% 
  unnest(cols = c(reviews))

```

